---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/vincenzocoia/powers.svg?branch=master)](https://travis-ci.org/vincenzocoia/powers)

__Note__: This R package is not mean to be "serious". It's just to show you are kinda cool and you can develop simple packages :cool:. 

# gapminderplus

This is an R package that has extended the gapminder dataset. This package also has included a simple `subset_country()` function which returns the mini dataset that was required for as many countries possible.

## Installation

You can install powers from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("STAT545-UBC-students/hw07-zeeva85/gapminderplus")
```

## Example

See the vignette for more extensive use, but here's an example:

```{r example, eval=T}
library(gapminderplus)


head(gapminder2)
tail(gapminder3)

# Enter empty value to end prompt
gapminderplus::subset_country()
gapminderplus::subset_country2()


## Console view

# 1: Malaysia
# 2: 
# Read 1 item
  
```

## For Developers

(Again, I don't actually intend for anyone to develop this silly and cool package, but if I did, here's what I'd write.)

Develop the subset function to accept values within its function and console. Add additional dataset available in the `data-raw` folder to the `gapminder2` dataset. 
